### 2021-04-06 paper/ase21/abstract.tex
[ASE21] Intro

  To alleviate this problem, we propose $\tool$, a JavaScript Specification Type
  Analyzer using Refinement.  It is the first tool that performs \textit{type
  analysis} on JavaScript specifications and detects specification bugs using
  \textit{bug checkers}.  For a given specification, our tool first compiles
  each abstract algorithm written in a structured natural language to the
  corresponding function of $\ires$, which is an untyped intermediate
  representation for ECMAScript.  Then, it performs type analysis for compiled
  functions with specification types defined in ECMAScript.  Based on the result
  of type analysis, $\tool$ detects specification bugs using four different bug
  checkers.  Moreover, to increase precision of type analysis, we also present
  \textit{refinement for type analysis}, which prunes out infeasible abstract
  states by using conditions of assertions and branches.  We evaluated $\tool$
  with all \inred{787} different versions of ECMAScript existed in the official
  repository for the recent three years (\inred{from 20 March 2018 to 9 March
  2021}).  Our tool detected \inred{XXX} specification bugs including only
  \inred{XXX} false alarms caused by the imprecision of type analysis.  Among
  \inred{XXX} true alarms, \inred{XXX} bugs are resolved after existing for
  \inred{XXX} days on average and \inred{XX} bugs still exist in the latest
  version of ECMAScript for \inred{XXX} days.  We reported all \inred{XX} newly
  found bugs and they are confirmed by the committee.
\end{abstract}

>>>>

  To alleviate this problem, we propose $\tool$, a JavaScript Specification Type
  Analyzer using Refinement.  It is the first tool that performs \textit{type
  analysis} on JavaScript specifications and detects specification bugs using
  \textit{bug detector}.  For a given specification, our tool first compiles
  each abstract algorithm written in a structured natural language to the
  corresponding function of $\ires$, which is an untyped intermediate
  representation for ECMAScript.  Then, it performs type analysis for compiled
  functions with specification types defined in ECMAScript.  Based on the result
  of type analysis, $\tool$ detects specification bugs using the bug detector
  consisting of four different checkers.  Moreover, to increase precision of
  type analysis, we also present \textit{condition-based refinement} for type
  analysis, which prunes out infeasible abstract states by using conditions of
  assertions and branches.  We evaluated $\tool$ with all \inred{XXX} different
  versions existed in the official ECMAScript repository for the recent
  \inred{three years from 2018 to 2021}.  Our tool detected \inred{XXX}
  specification bugs including only \inred{XXX} false alarms caused by the
  imprecision of type analysis in \inred{XX} minutes on average.  Among
  \inred{XXX} true alarms, \inred{XXX} bugs are resolved after existing for
  \inred{XXX} days on average and \inred{XX} bugs still exist in the latest
  version of ECMAScript for \inred{XXX} days.  We reported all \inred{XX} newly
  found bugs and they are confirmed by the committee.
\end{abstract}

### 2021-04-06 paper/ase21/intro.tex
[ASE21] Intro

\begin{itemize}
  \item JavaScript is one of mainstream programming languages not only in
    client-side programming but also in serever-side programming and even
    embedded systems.

  \item Various JavaScript engines are developed and maintained in various
    fields and they must conform to the syntax and semantics described in
    ECMAScript, the standard specification of JavaScript.

  \item Since an incorrect description in ECMAScript can lead to the wrong
    implementation of JavaScript engines, it is important to check the
    correctness of ECMAScript.

  \item However, all the specification updates are currently manually checked by
    the Ecma Technical Committee 39 (TC39) without any automated tools.

  \item Moreover, in late 2014, the committee announced yearly release cadence
    and open development process of ECMAScript to quickly adapt to an evolving
    development environment.

  \item Thus, the manual checking becoems more labor-intensive and error-prone.

  \item To alleviate this problem, we propose $\tool$, an ECMAScript Static
    Checker based on Refinement Types.  Our tool performs the following three
    steps for a given specification: 1) to convert abstract algorithms in the
    specification to untyped intermediate representation, 2) to extract type
    information of data structures used in the specification, and 3) to perform
    type analysis with the extracted type information to detect specification
    errors.  Moreover, we use \textit{refinement types} over the extracted type
    information to reduce false alarms.  \inred{TODO: explanation of refinement
    types.}
\end{itemize}

Our main contributions are as follows:
\begin{itemize}
  \item We implemented $\tool$, which is the first tool that statically checks the
    correctness of JavaScript language specifications using type analysis.  It
    can detect variuos kinds of specification errors including \inred{reference
    errors, $\cdots$}.
  \item We present \inred{...} to increase the precision of type analysis.
    \inred{$\cdots$}.
  \item We evaluate $\tool$ with \inred{XXX different versions of ECMAScript in
    the official repository between 2018 June and 2021 March.} Among \inred{XXX}
    known specification errors, our tool detected \inred{XXX} errors with
    \inred{XXX} false alarms.  Moreover, $\tool$ detected \inred{X} new
    specification errors in the draft of next release of ECMAScript (ES12,
    2021).
\end{itemize}

>>>>

JavaScript is one of the most popular programming languages.  According to the
2020 State of the Octoverse\footnote{https://octoverse.github.com/}, which is
the annual report of GitHub, the most dominated programming language in GitHub
repositories was JavaScript since 2014 to 2020.  While JavaScript was initially
designed for client-side programming in web browsers, now it is widely used in
server-side programming~\cite{nodejs} and even in embedded
systems~\cite{espruino, tessel2, moddable}.  Thus, its engines are also
developed and maintained in diverse fields conforming to ECMAScript, the
JavaScript standard specification that describes the syntax and semantics of
JavaScript.

The correctness of ECMAScript becomes more important because an incorrect
description of syntax or semantics in the specification can lead to the wrong
implementation of existing JavaScript engines used in various fields.  However,
all the specification updates are currently manually checked by the Ecma
Technical Committee 39 (TC39) without any automated tools.  This manual checking
process is obviously labor-intensive and also error-prone thus the current
JavaScript specification is vulnerable to specification bugs.  Besides, in late
2014, the committee announced yearly release cadence and open development
process of ECMAScript to quickly adapt to an evolving development environment.
According to \citet{jiset}, the average number of updated steps of abstract
algorithms between consecutive releases from ES7 (2016) to ES10 (ES2019) is
9645.5.  In the official repository of ECMAScript, \inred{X,XXX} pull requests
and \inred{X,XXX} commits exist in the master branch.  Therefore, it makes more
difficult to manually check all the specification updates using limited human
resources.

Unfortunately, there is no existing tool to automatically detect bugs in the
rapidly evolved JavaScript specifications.  Thus, the committee of ECMAScript
have tried to resolve this problem using additional annotations in abstract
algorithms.  Additional annotations make the specification more readable and
also they are useful for the specification-based tools such as JavaScript
engines~\cite{v8, graaljs, qjs, moddable}, static analyzers~\cite{safe, tajs,
jsai, wala}, and verification tools~\cite{javert}.  Thus, they decided to
manually insert two different annotations: 1) \textit{assertions} to denotes the
assumptions in a certain point of abstract algorithms, and 2) two different
\textit{prefixes} $\code{?}$ and $\code{!}$ to represent whether completion
records might be abrupt or not.  For example, $\code{"Assert: Type(O) is
Object"}$ denotes that the variable $\code{O}$ always has $\code{Object}$ values
at this point and $\code{"? GetV(V, P)"}$ denotes that return values of
$\code{GetV(V, P)}$ might be abrupt completions.  Moreover, they recently
started the internal discussion of manual type annotations for variables,
parameters, and return values for each abstract algorithm.  However, to manually
annotate types for all of them without any automated tool is also
labor-intensive and error-prone.  Furthermore, even though the such manual type
annotations can give more information for manual checking of specification
updates, it still does not provide any automatic approach to detect
specification bugs.

To alleviate this problem, we propose a tool $\tool$, a \textbf{J}avaScript
\textbf{S}pecification \textbf{T}ype \textbf{A}nalyzer using
\textbf{R}efinement.  The main idea of our tool is to perform \textit{type
analysis} for JavaScript specifications to statically detect type-related
specification bugs in an automatic way.  However, it is difficult to directly
perform type analysis to ECMAScript because its abstract algorithms are written
in a natural language.  For a decade, researchers~\cite{lambdajs, jscert, kjs}
have tried to formally define various mechanized JavaScript specification for a
specific version of ECMAScript by hand.  However, the manual formalization is
not suitable for the automatic detection of bugs in the rapidly evolved
JavaScript specifications.  On the other hand, several approaches to utilize
information directly extracted from specifications written in a structured
natural language are recently presented in diverse fields such as system
architectures~\cite{x86, arm}, network protocols~\cite{basespec}, and language
specifications~\cite{spectest}.  For JavaScript, \citet{jiset} presents $\jiset$
that automatically compiles each abstract algorithm written in a structured
natural language to the corresponding function of $\ires$, an untyped
intermediate representation for ECMAScript.  Therefore, we leverage this tool to
automatically get mechanized specifications for JavaScript.

For the compiled mechanized specifications, $\tool$ performs type analysis for
compiled functions with specification types defined in ECMAScript.  ECMAScript
contains not only JavaScript language types but also specification types such as
abstract syntax trees (ASTs), internal records (i.e. environments, completions,
or property descriptors), and internal lists.  Our tool extract syntax and
table-based type information from ECMAScript and constructs type hierarchy and
fields for ASTs and records.  Based on the extracted types, $\tool$ performs
type analysis and detects specification bugs using a \textit{bug detector}
consisting of four different checkers: 1) reference checker, 2) arity checker,
3) operator type checker, and 4) assertion checker.  Moreover, to increase
precision of type analysis, we also present \textit{condition-based refinement}
for type analysis on ECMAScript. Its main concept is to prunes out infeasible
abstract states by using conditions of assertions and branches.  The refinement
technique can reduce false alarms caused by spurious types inferred by imprecise
analysis.  We evaluate our tool with all \inred{XXX} different versions existed
in the official ECMAScript repository for the recent \inred{three years from
2018 to 2021}.

In summary, our main contributions are as follows:
\begin{itemize}
  \item We present $\tool$, which is the first tool that performs \textit{type
    analysis} on ECMAScript to check the the correctness of JavaScript language
    specifications.  $\tool$ automatically detects specification bugs via the
    \textit{bug detector} consisting of four different checkers: 1) reference
    checker, 2) arity checker, 3) operator type checker, and 4) assertion
    checker.
  \item We present \textit{condition-based refinement} for type analysis of
    ECMAScript to reduce false alarms by increasing the analysis precision.  Its
    main idea is to prune out infeasible abstract states by using conditions of
    assertions and branches.
  \item We demonstrate the practicality of $\tool$. For recent \inred{XXX}
    different versions of ECMAScript, our tool detected \inred{XXX}
    specification bugs including only \inred{XXX} false alarms caused by the
    imprecision of type analysis in \inred{XX} minutes on average.  Among
    \inred{XXX} true alarms, \inred{XXX} bugs are resolved after existing for
    \inred{XXX} days on average and \inred{XX} bugs still exist in the latest
    version of ECMAScript for \inred{XXX} days.  We reported all \inred{XX}
    newly found bugs and they are confirmed by the committee.
\end{itemize}

### 2021-04-06 paper/ase21/related.tex
[ASE21] Intro

\begin{itemize}
  \item JISET: JavaScript IR-based Semantics Extraction Toolchain~\cite{jiset}
\end{itemize}

>>>>

\begin{itemize}
  \item Abstract Interpretation~\cite{ai1977, ai1992}
  \item JISET: JavaScript IR-based Semantics Extraction Toolchain~\cite{jiset}
  \item JavaScript Manual Mechanized Specification:
    \begin{itemize}
      \item The Essence of Javascript~\cite{lambdajs}
      \item A Trusted Mechanised JavaScript Specification~\cite{jscert}
      \item JaVerT: JavaScript Verification Toolchain~\cite{javert}
      \item KJS: A complete formal semantics of JavaScript~\cite{kjs}
      \item JSExplain: A Double Debugger for JavaScript~\cite{jsexplain}
      \item JEST: N+ 1-version Differential Testing of Both JavaScript Engines
        and Specification~\cite{jest}
    \end{itemize}
  \item Automatic Mechanized Specification for others:
    \begin{itemize}
      \item Automatic extraction of x86 formal semantics from its natural
        language description~\cite{x86}
      \item Formal semantics extraction from natural language specifications for
        ARM~\cite{arm}
      \item SpecTest: Specification-Based Compiler Testing~\cite{spectest}
      \item BASESPEC: Comparative Analysis of Baseband Software and Cellular
        Specifications for L3 Protocols~\cite{basespec}
    \end{itemize}
\end{itemize}
